Project 2

### 2015-04-24 project2/paper/main.tex
Adding some better headings
Fixing the date
Stubbing out the last section

\title{Project 2}
\author{Chip Bell}
\date{March 31, 2015}
\maketitle

@@

\section{Current and Remaining Work}
Currently, the app is simply mapping stations and labeling them based on information provided by the API. The entirety
of data analysis is complete, and can be
viewed within the \texttt{queries} directory, along with the \texttt{utils}. A few data files are strewn about the
codebase as well. The WMATA API query code is stored within the \texttt{wmata} folder.

I have also copied some code over from the first project since it will be applicable, such as a discrete event queue.
However, the \texttt{Track} class remains to be written and is integral to the application, along with the \texttt{Train}
class. Furthermore, the actual
train scheduling algorithm itself needs to be written. However, the current application is deployed here
\cite{aprilandchip}.

>>>>

\title{Project 2}
\author{Chip Bell}
\date{April 24, 2015}
\maketitle

@@

\section{Current Build and Instructions}
The functioning simulation is currently hosted at \cite{aprilandchip}. On this page, you can see trains moving through
the metro system, with real-time statistics as trains reach the other side. Also, tracks can be disabled via the
checkboxes at the bottom, which will influence trains in real-time. The map itself is interactive, and provides a few
glimpses into the system. Clicking on a station gives you the name, and clicking on a connection tells you current stats
at that section of track.

Also within the project directory that has been uploaded with the submission are some of the data analysis tools I've
built for performing queries, and cleaning data. These can be found in the \texttt{queries} and \texttt{utils}
directory of the project. Among the scripts found include bash scripts for file templating (for building queries
dynamically), templated js scripts for querying a mongo database, along with a few Python scripts for performing data
cleanup (like boxcar filtering for smoothing, and simple binning for histograms).

\section{Results and Conclusions}
One of the goals for this project was to better understand the metro system as a whole. In particular, I wanted to
discover how accurate WMATA was at predicting trains, and also how robust their scheduling was to unpredicted track
unavailability. WMATA provides their own estimates of how often trains occur \cite{metroschedule}, along with between
station times from any station to another \cite{rosslyntime}. This gives us plenty of room for comparison.

% Talking points
% - Average between station time
% - Rosslyn to Stadium Armory time is consistent
% - Robustness to changes in track availability

Unsurprisingly, WMATA plans its trains effectively to be robust to a fair amount track outages, while still providing
the timings estimated on their website.
